---
title: "Analysis of WEBS Survey Data"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries and import, echo = TRUE, results = 'hide', collapse = TRUE, message = FALSE, warning = FALSE}
# Libraries
library(tidyverse)
library(cowplot)

# Color palette
three_colors = c("#1b9e77", "#785ef0", "#e6ab02")
four_colors = c("#1b9e77", "#d95f02", "#7570b3", "#e7298a")
five_colors = c("#1b9e77", "#d95f02", "#7570b3", "#e7298a", "#e6ab02")
six_colors = c("#1b9e77", "#d95f02", "#7570b3", "#e7298a", "#e6ab02", "#66a61e")

# Modules Completed
completed <-
  read.csv("query_outputs/query_outputs2/module_survey_completion.csv") 
self_reported <-
  read.csv("query_outputs/query_outputs2/participation_counts_modules.csv") 

# Module Efficacy
module1_training <- read.csv("query_outputs/query_outputs2/module1_training.csv") 
module2_training <- read.csv("query_outputs/query_outputs2/module2_training.csv") 
module3_training <- read.csv("query_outputs/query_outputs2/module3_training.csv") 
module4_training <- read.csv("query_outputs/query_outputs2/module4_training.csv") 

# Spider Curiosity
spider_curiosity_individual <- read.csv("query_outputs/query_outputs2/spider_curiosity_individual.csv")
```

# Modules Completed {.tabset}

First, I wanted to see how many participants completed the workshop modules. I could achieve this in two different ways:

* The number of surveys completed after each module

* The number of self-reported (from the post-training survey) completed module workshops

*The numbers on the bars represent the raw number of participants.*

## Completed Module Surveys

**Spring 2022 had the highest module survey completion.**

```sql
WITH module_summary AS(
	SELECT
	  COALESCE(m1.recipient_id, m2.recipient_id, m3.recipient_id, m4.recipient_id) AS recipient_id,
	  p.iteration,
	  CASE WHEN m1.recipient_id IS NULL THEN 0 ELSE 1 END AS module1,
	  CASE WHEN m2.recipient_id IS NULL THEN 0 ELSE 1 END AS module2,
	  CASE WHEN m3.recipient_id IS NULL THEN 0 ELSE 1 END AS module3,
	  CASE WHEN m4.recipient_id IS NULL THEN 0 ELSE 1 END AS module4,
	  (CASE WHEN m1.recipient_id IS NULL THEN 0 ELSE 1 END +
	   CASE WHEN m2.recipient_id IS NULL THEN 0 ELSE 1 END +
	   CASE WHEN m3.recipient_id IS NULL THEN 0 ELSE 1 END +
	   CASE WHEN m4.recipient_id IS NULL THEN 0 ELSE 1 END) AS module_count
	FROM training.module1 m1
	FULL JOIN training.module2 m2 
	  ON m1.recipient_id = m2.recipient_id
	FULL JOIN training.module3 m3 
	  ON COALESCE(m1.recipient_id, m2.recipient_id) = m3.recipient_id
	FULL JOIN training.module4 m4 
	  ON COALESCE(m1.recipient_id, m2.recipient_id, m3.recipient_id) = m4.recipient_id
	-- Add the join to participants
	LEFT JOIN training.participants p 
	  ON COALESCE(m1.recipient_id, m2.recipient_id, m3.recipient_id, m4.recipient_id) = p.recipient_id
	GROUP BY 
	  COALESCE(m1.recipient_id, m2.recipient_id, m3.recipient_id, m4.recipient_id),
	  p.iteration,
	  m1.recipient_id, m2.recipient_id, m3.recipient_id, m4.recipient_id
	ORDER BY recipient_id
)

SELECT iteration, module_count, COUNT(*) AS n_participants
FROM module_summary
GROUP BY iteration, module_count
ORDER BY iteration, module_count;
```

```{r modules completed, echo = TRUE, collapse = TRUE, message = FALSE, warning = FALSE, fig.align="center", fig.width = 7, fig.height = 5}
# set factor level order
completed <- completed %>% 
  mutate(module_count = factor(module_count),
         module_count = fct_relevel(module_count, "4", "3", "2", "1"),
         iteration = factor(iteration),
         iteration = fct_relevel(iteration, 
                                 "Spring 2023", "Fall 2022", "Spring 2022"))

# Sets the positions for where to put the raw numebrs in the graph
completed$position <- c(0.12, 0.36, 0.7, 0.05, 0.175, 
                        0.325, 0.65, 0.097, 0.24, 0.65)

# Makes the graph
completed %>% 
  ggplot() +
    geom_bar(aes(x = n_participants, y = iteration, fill = module_count), 
             position = "fill", stat = "identity") +
    geom_text(aes(x = position, y = iteration, label = n_participants)) +
    scale_x_continuous(labels = scales::percent) +
  scale_fill_manual("No. Modules Surveys Completed", 
                 values = four_colors) +
  xlab("") +
  ylab("") +
  theme_classic() +
  theme(legend.position = "top",
        axis.text = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 12, color = "black")) +
  guides(fill = guide_legend(reverse=TRUE))
```

---

## Self-Reported in Post-Survey

**Spring 2022 had the highest participation in the post-training survey.**

```sql
SELECT answer_count, iteration, COUNT(*) AS n_participants
FROM(
	SELECT posttest.recipient_id, iteration, COUNT(answer) AS answer_count
	FROM training.posttest
	JOIN training.participants
	ON posttest.recipient_id = participants.recipient_id
	JOIN training.questions
	ON posttest.question_id = questions.question_id
	WHERE posttest.question_id LIKE 'participation%'
	AND posttest.question_id NOT LIKE 'participation5'
	GROUP BY posttest.recipient_id, iteration
)
GROUP BY answer_count, iteration
ORDER BY iteration, answer_count;
```

```{r modules self-reported, echo = TRUE, collapse = TRUE, message = FALSE, warning = FALSE, fig.align="center", fig.width = 7, fig.height = 5}
# set factor level order
self_reported <- self_reported %>% 
  mutate(answer_count = factor(answer_count),
         answer_count = fct_relevel(answer_count, "4", "3", "2", "1"),
         iteration = factor(iteration),
         iteration = fct_relevel(iteration, 
                                 "Spring 2023", "Fall 2022", "Spring 2022"))

# Sets the positions for where to put the raw numebrs in the graph
self_reported$position <- c(0.31, 0.81, 0.07, 0.57, 
                              0.02, 0.09, 0.54, 0.98)

# Makes the graph
self_reported %>% 
  ggplot() +
    geom_bar(aes(x = n_participants, y = iteration, fill = answer_count), 
             position = "fill", stat = "identity") +
    geom_text(aes(x = position, y = iteration, label = n_participants)) +
    scale_x_continuous(labels = scales::percent) +
  scale_fill_manual("No. Self-Reported Modules Completed", 
                 values = four_colors) +
  xlab("") +
  ylab("") +
  theme_classic() +
  theme(legend.position = "top",
        axis.text = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 12, color = "black")) +
  guides(fill = guide_legend(reverse=TRUE))
```

---
# Module Efficacy  {.tabset}

Next, I wanted to explore the surveys provided after each module to look at the effectiveness of the module. 

*The numbers to the right indicate the number of survey responses associated with each statement.*

```sql
SELECT iteration, module, module1.question_id, definition1, definition2, definition3, definition4, definition5, question, answer, COUNT(module1.recipient_id) AS response
FROM training.module1
JOIN training.participants
ON module1.recipient_id = participants.recipient_id
JOIN training.questions
ON module1.question_id = questions.question_id
GROUP BY iteration, module, module1.question_id, definition1, definition2, definition3, definition4, definition5, question, answer
ORDER BY iteration, question_id, answer;
```

## All Levels

**Students were a little less certain of the fourth module. Interestingly, none felt that they strongly disagreed with any statement in the fourth module.**

```{r module efficacy, echo = TRUE, collapse = TRUE, message = FALSE, warning = FALSE, fig.align="center", fig.width = 11, fig.height = 9}
# Module 1
module1_training <- module1_training %>% 
  # Refactor to include the level indications
  mutate(answer = ifelse(answer == 1, "Strongly \ndisagree",
                  ifelse(answer == 2, "Somewhat \ndisagree",
                  ifelse(answer == 3, "Neither agree \nnor disagree", 
                  ifelse(answer == 4, "Somewhat \nagree", 
                  ifelse(answer == 5, "Strongly \nagree", "NA"))))),
         answer = fct_relevel(answer, "Strongly \nagree", "Somewhat \nagree", 
                              "Neither agree \nnor disagree", 
                              "Somewhat \ndisagree", "Strongly \ndisagree"),
         iteration, fct_relevel(iteration, "Spring 2023", "Fall 2022", "Spring 2022")) %>% 
  dplyr::select(iteration, question_id, question, answer, response) %>% 
  # Counts the number of participants selecting each level for each question
  group_by(question_id, question, answer) %>% 
  summarize(response = sum(response))

# Count the number of responses for that question
sum_module1 <- module1_training %>% 
  group_by(question) %>% 
  summarize(total = sum(response)) %>% 
  mutate(y = 1.1)
  
# Graph Modules 1
module1_graph <- ggplot() +
    geom_bar(aes(x = response, y = question, fill = answer), 
             position = "fill", stat = "identity", data = module1_training) +
    geom_text(aes(x = y, y = question, label = total), data = sum_module1) +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_manual("Level of \nAgreement", 
                 values = five_colors) +
  xlab("") +
  ylab("Module 1") +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_blank(),
        axis.title.y = element_text(size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        legend.text = element_text(size = 10, color = "black"),
        legend.title = element_text(size = 10, color = "black")) +
  guides(fill = guide_legend(reverse = TRUE, nrow = 2))

# Module 2
module2_training <- module2_training %>% 
  # Refactor to include the level indications
  mutate(answer = ifelse(answer == 1, "Strongly \ndisagree",
                  ifelse(answer == 2, "Somewhat \ndisagree",
                  ifelse(answer == 3, "Neither agree \nnor disagree", 
                  ifelse(answer == 4, "Somewhat \nagree", 
                  ifelse(answer == 5, "Strongly \nagree", "NA"))))),
         answer = fct_relevel(answer, "Strongly \nagree", "Somewhat \nagree", 
                              "Neither agree \nnor disagree", 
                              "Somewhat \ndisagree", "Strongly \ndisagree"),
         iteration, fct_relevel(iteration, "Spring 2023", "Fall 2022", "Spring 2022")) %>% 
  dplyr::select(iteration, question_id, question, answer, response) %>% 
  # Counts the number of participants selecting each level for each question
  group_by(question_id, question, answer) %>% 
  summarize(response = sum(response))

# Count the number of responses for that question
sum_module2 <- module2_training %>% 
  group_by(question) %>% 
  summarize(total = sum(response)) %>% 
  mutate(y = 1.1)
  
# Module 2 Graph
module2_graph <- ggplot() +
    geom_bar(aes(x = response, y = question, fill = answer), 
             position = "fill", stat = "identity", data = module2_training) +
    geom_text(aes(x = y, y = question, label = total), data = sum_module2) +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_manual("Level of Agreement", 
                 values = five_colors) +
  xlab("") +
  ylab("Module 2") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.y = element_text(size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        legend.text = element_text(size = 10, color = "black"),
        legend.title = element_text(size = 10, color = "black")) +
  guides(fill = guide_legend(nrow = 2))

# Module 3
module3_training <- module3_training %>% 
  # Refactor to include the level indications
  mutate(answer = ifelse(answer == 1, "Strongly \ndisagree",
                  ifelse(answer == 2, "Somewhat \ndisagree",
                  ifelse(answer == 3, "Neither agree \nnor disagree", 
                  ifelse(answer == 4, "Somewhat \nagree", 
                  ifelse(answer == 5, "Strongly \nagree", "NA"))))),
         answer = fct_relevel(answer, "Strongly \nagree", "Somewhat \nagree", 
                              "Neither agree \nnor disagree", 
                              "Somewhat \ndisagree", "Strongly \ndisagree"),
         iteration, fct_relevel(iteration, "Spring 2023", "Fall 2022", "Spring 2022")) %>% 
  dplyr::select(iteration, question_id, question, answer, response) %>% 
  # Counts the number of participants selecting each level for each question
  group_by(question_id, question, answer) %>% 
  summarize(response = sum(response))

# Count the number of responses for that question
sum_module3 <- module3_training %>% 
  group_by(question) %>% 
  summarize(total = sum(response)) %>% 
  mutate(y = 1.1)
  
# Module 3 Graph
module3_graph <- ggplot() +
    geom_bar(aes(x = response, y = question, fill = answer), 
             position = "fill", stat = "identity", data = module3_training) +
    geom_text(aes(x = y, y = question, label = total), data = sum_module3) +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_manual("Level of Agreement", 
                 values = five_colors) +
  xlab("") +
  ylab("Module 3") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.y = element_text(size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        legend.text = element_text(size = 10, color = "black"),
        legend.title = element_text(size = 10, color = "black")) +
  guides(fill = guide_legend(nrow = 2))

# Module 4
module4_training <- module4_training %>% 
  filter(answer != "NULL") %>% 
  # Refactor to include the level indications
  mutate(answer = ifelse(answer == 1, "Strongly \ndisagree",
                  ifelse(answer == 2, "Somewhat \ndisagree",
                  ifelse(answer == 3, "Neither agree \nnor disagree", 
                  ifelse(answer == 4, "Somewhat \nagree", 
                  ifelse(answer == 5, "Strongly \nagree", "NA"))))),
         answer = fct_relevel(answer, "Strongly \nagree", "Somewhat \nagree", 
                              "Neither agree \nnor disagree", 
                              "Somewhat \ndisagree", "Strongly \ndisagree"),
         iteration, fct_relevel(iteration, "Spring 2023", "Fall 2022", "Spring 2022")) %>% 
  dplyr::select(iteration, question_id, question, answer, response) %>% 
  # Counts the number of participants selecting each level for each question
  group_by(question_id, question, answer) %>% 
  summarize(response = sum(response))

# Count the number of responses for that question
sum_module4 <- module4_training %>% 
  group_by(question) %>% 
  summarize(total = sum(response)) %>% 
  mutate(y = 1.1)
  
# Module 4 Graph
module4_graph <- ggplot() +
    geom_bar(aes(x = response, y = question, fill = answer), 
             position = "fill", stat = "identity", data = module4_training) +
    geom_text(aes(x = y, y = question, label = total), data = sum_module4) +
  scale_x_continuous(labels = scales::percent) +
    scale_fill_manual("Level of Agreement", 
                 values = five_colors) +
  xlab("") +
  ylab("Module 4") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title.y = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 10, color = "black"),
        legend.title = element_text(size = 10, color = "black")) +
  guides(fill = guide_legend(nrow = 2))

# Combine the four module responses
plot_grid(module1_graph, module2_graph, module3_graph, module4_graph, 
          ncol=1, align="v", rel_heights = c(2, 1.2, 1.2, 1.4))
```

---

## Generalized to Disgree/Neutral/Agree

**Students were a little less certain of the fourth module.**

```{r module efficacy simpler, echo = TRUE, collapse = TRUE, message = FALSE, warning = FALSE, fig.align="center", fig.width = 11, fig.height = 9}
# Module 1
# Regroup into Agree, Neutral, and Disagree
module1_simpler <- module1_training %>% 
  mutate(answer = ifelse(answer == "Strongly \nagree" | 
                         answer == "Somewhat \nagree", 
                         "Agree",
                  ifelse(answer == "Strongly \ndisagree" | 
                         answer == "Somewhat \ndisagree", 
                         "Disagree", "Neutral")),
         answer = fct_relevel(answer, "Agree", "Neutral", "Disagree")) %>% 
  # Recount
  group_by(question_id, question, answer) %>% 
  summarize(response = sum(response))

# Module 1 Graph
module1_simpler_graph <- ggplot() +
    geom_bar(aes(x = response, y = question, fill = answer), 
             position = "fill", stat = "identity", data = module1_simpler) +
    geom_text(aes(x = y, y = question, label = total), data = sum_module1) +
  scale_x_continuous(labels = scales::percent) +
    scale_fill_manual("Level of Agreement", 
                 values = three_colors) +
  xlab("") +
  ylab("Module 1") +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_blank(),
        axis.title.y = element_text(size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        legend.text = element_text(size = 10, color = "black"),
        legend.title = element_text(size = 10, color = "black")) +
  guides(fill = guide_legend(reverse=TRUE))

# Module 2
# Regroup into Agree, Neutral, and Disagree
module2_simpler <- module2_training %>% 
  mutate(answer = ifelse(answer == "Strongly \nagree" | 
                         answer == "Somewhat \nagree", 
                         "Agree",
                  ifelse(answer == "Strongly \ndisagree" | 
                         answer == "Somewhat \ndisagree", 
                         "Disagree", "Neutral")),
         answer = fct_relevel(answer, "Agree", "Neutral", "Disagree")) %>% 
  # Recount
  group_by(question_id, question, answer) %>% 
  summarize(response = sum(response))

# Module 2 Graph
module2_simpler_graph <- ggplot() +
    geom_bar(aes(x = response, y = question, fill = answer), 
             position = "fill", stat = "identity", data = module2_simpler) +
    geom_text(aes(x = y, y = question, label = total), data = sum_module2) +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_manual("Level of Agreement", 
                 values = three_colors) +
  xlab("") +
  ylab("Module 2") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.y = element_text(size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        legend.text = element_text(size = 10, color = "black"),
        legend.title = element_text(size = 10, color = "black")) 

# Module 3
# Regroup into Agree, Neutral, and Disagree
module3_simpler <- module3_training %>% 
  mutate(answer = ifelse(answer == "Strongly \nagree" | 
                         answer == "Somewhat \nagree", 
                         "Agree",
                  ifelse(answer == "Strongly \ndisagree" | 
                         answer == "Somewhat \ndisagree", 
                         "Disagree", "Neutral")),
         answer = fct_relevel(answer, "Agree", "Neutral", "Disagree")) %>% 
  # Recount
  group_by(question_id, question, answer) %>% 
  summarize(response = sum(response))

# Module 3 Graph
module3_simpler_graph <- ggplot() +
    geom_bar(aes(x = response, y = question, fill = answer), 
             position = "fill", stat = "identity", data = module3_simpler) +
    geom_text(aes(x = y, y = question, label = total), data = sum_module3) +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_manual("Level of Agreement", 
                 values = three_colors) +
  xlab("") +
  ylab("Module 3") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.y = element_text(size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        legend.text = element_text(size = 10, color = "black"),
        legend.title = element_text(size = 10, color = "black"))

# Module 4
# Regroup into Agree, Neutral, and Disagree
module4_simpler <- module4_training %>% 
  mutate(answer = ifelse(answer == "Strongly \nagree" | 
                         answer == "Somewhat \nagree", 
                         "Agree",
                  ifelse(answer == "Strongly \ndisagree" | 
                         answer == "Somewhat \ndisagree", 
                         "Disagree", "Neutral")),
         answer = fct_relevel(answer, "Agree", "Neutral", "Disagree")) %>% 
  # Recount
  group_by(question_id, question, answer) %>% 
  summarize(response = sum(response))

# Module 4 Graph
module4_simpler_graph <- ggplot() +
    geom_bar(aes(x = response, y = question, fill = answer), 
             position = "fill", stat = "identity", data = module4_simpler) +
    geom_text(aes(x = y, y = question, label = total), data = sum_module4) +
  scale_x_continuous(labels = scales::percent) +
    scale_fill_manual("Level of Agreement", 
                 values = three_colors) +
  xlab("") +
  ylab("Module 4") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title.y = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 10, color = "black"),
        legend.title = element_text(size = 10, color = "black")) 

# Combine the four module responses
plot_grid(module1_simpler_graph, module2_simpler_graph, 
          module3_simpler_graph, module4_simpler_graph, 
          ncol=1, align="v", rel_heights = c(1.6, 1.2, 1.2, 1.4))
```

---



# Spiders - Curiosity {.tabset}

The post-training survey included statements of curiosity toward spiders where participants were asked to provide their level of agreement to each statement. 

## Pre-Post - Individual Statements

```sql
SELECT pretest.recipient_id, iteration, pretest.question_id, question, answer_type, definition1, definition2, definition3, definition4, definition5, pretest.answer AS pre_answer, posttest.answer AS post_answer, posttest.answer-pretest.answer AS change
FROM training.pretest
JOIN training.posttest
ON pretest.recipient_id = posttest.recipient_id AND pretest.question_id = posttest.question_id
JOIN training.questions
ON pretest.question_id = questions.question_id
JOIN training.participants
ON pretest.recipient_id = participants.recipient_id
WHERE pretest.answer IS NOT NULL AND posttest.answer IS NOT NULL
AND questions.question_type = 'Spider Curiosity'
ORDER BY recipient_id, question_id;
```

```{r spider_curiosity_individual stats, include = FALSE}
# Vector of question IDs
question_ids <- paste0("prepost26_", 1:7)

# Create summary table
spider_curiosity_table <- purrr::map_dfr(question_ids, function(qid) {
  data <- spider_curiosity_individual %>%
    filter(question_id == qid)
  
  ttest <- t.test(data$pre_answer, data$post_answer, paired = TRUE)
  p_val <- ttest$p.value
  p_val_bonf <- p.adjust(p_val, method = "bonferroni", n = length(question_ids))
  
  tibble::tibble(
    question_id = qid,
    question = unique(data$question),
    n = nrow(data),
    pre_mean = round(mean(data$pre_answer), 3),
    pre_se = round(plotrix::std.error(data$pre_answer), 3),
    post_mean = round(mean(data$post_answer), 3),
    post_se = round(plotrix::std.error(data$post_answer), 3),
    p_value = round(p_val, 3),
    p_value_bonferroni = round(p_val_bonf, 3)
  )
})

```

```{r spider_curiosity_individual graph, echo = TRUE, collapse = TRUE, message = FALSE, warning = FALSE, fig.align="center", fig.width = 11, fig.height = 7}
spider_curiosity_individual_sum <- spider_curiosity_individual %>% 
  group_by(question_id, question) %>% 
  summarize(mean_change = mean(change),
            se_change = plotrix::std.error(change)) %>% 
  mutate(y = 1.2,
         y2 = 1,
         question = factor(question),
         question = fct_relevel(question,
                                "I would like to read more about spiders.",
                                "I would like to know more about spiders.", 
                                "I would like to know more about how scientists study spiders.",
                                "Greater attention should be given to spider protection.",
                                "Spiders are interesting animals.", 
                                "People should use fewer chemicals in order to allow spiders to live.",
                                "I would like to watch a spider constructing its web."))

spider_curiosity_individual_sum$stats <- c("", "", "", ". / NS", "", "", "")
spider_curiosity_individual_sum$post_mean <- spider_curiosity_table$post_mean

spider_curiosity_individual_sum %>% 
  ggplot() +
  geom_point(aes(x = mean_change, y = question, color = question)) +
  geom_errorbar(aes(xmax = mean_change + 1.96 * se_change, 
                    xmin = mean_change - 1.96 * se_change, 
                    y = question, color = question), width = 0.25) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_text(aes(x = y2, y = question, label = stats, 
                color = question), size = 4) +
  geom_text(aes(x = y, y = question, label = post_mean, 
                color = question), size = 3) +
  scale_x_continuous(limits = c(-0.7, 1.3), breaks = c(seq(-0.5, 1, 0.5))) +
  scale_color_manual(values = c("black", "black", "black", "#7570b3", "black", "black", "black")) +
  ylab("") +
  xlab("Change toward disagreement ------------- Change toward agreement") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y = element_text(size = 10, color = "black"),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.title.x = element_text(size = 10, color = "black"))
```

## ELE vs Modules Only - Composite Score
